DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2017-11-15 paper/cvpr2018/cvpr2018_draft.tex
figure caption draft

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small TODO: Pull figure caption goes here.}}
        \label{fig:pull_figure}
\end{figure}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{ {\small TODO: framework caption goes here.}}
        \label{fig:framework}
\end{figure*}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
        \caption{ {\small TODO: network detail.}}
        \label{fig:dataset}
\end{figure}
\subsection{SEG-LSTM Architecture}

@@

In addition to  historical trajectory information, the third architecture(SEG-LSTM) also fuses semantics of  historical frames as auxiliary information. The input to the bottom-most LSTM layer is the 3D occupancy of historical trajectory. The second LSTM layer fuses the outputs of the bottom-most LSTM with the frame's semantic information, which is extracted from the semantic segmentation through a four-layer CNN, to produce a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions,{x, y, w, h, dmin, dmax}. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance trajectory information and the semantic information. The LSTM part  and fully connected part is same as the one of above two architecture, and the CNN part is composed of four convolutional block. Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer. Each convolutional layer has four channels and 3×3 kernel. Results show that the SEG-LSTM model performs better than the other two temporal model.

@@

\subsection{Evaluation}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
        \caption{ {\small TODO: evaluation caption goes here.}}
        \label{fig:evaluation}
\end{figure}

>>>>

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small We propose a system to predict future trajectories of vehicles. Given a historical information, obtained by detection, tracking and semantic segmentation, a network based on Long Short Term Memory (LSTM) structure is trained to generate future information.}}
        \label{fig:pull_figure}
\end{figure}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{ {\small The framework of our vehicle future trajectory prediction system. The input is the sequence data from a synthetic scene in \cite{mueller2016benchmark}. Historical information are extracted by detection & tracking and semantic segmentation. All of the information is fed into our LSTM model to predict future trajectories.}}
        \label{fig:framework}
\end{figure*}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
        \caption{ {\small Different networks to predict future trajectory. Left: FrameToFrame, using historical trajectories with many-to-many LSTM to predict; Middle:FrameToSeq, using historical trajectories with many-to-many LSTM ; Right:SEG-LSTM, the proposed model by using historical trajectories and semantic segmentation information.}}
        \label{fig:dataset}
\end{figure}
\subsection{SEG-LSTM Architecture}

@@

In addition to  historical trajectory information, the third architecture(SEG-LSTM) also fuses semantics of  historical frames as auxiliary information. The input to the bottom-most LSTM layer is the 3D occupancy of historical trajectory. The second LSTM layer fuses the outputs of the bottom-most LSTM with the frame's semantic information, which is extracted from the semantic segmentation through a four-layer CNN, to produce a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions,{x, y, w, h, dmin, dmax}. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance trajectory information and the semantic information. The LSTM part  and fully connected part is same as the one of above two architecture, and the CNN part is composed of four convolutional block. Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer. Each convolutional layer has four channels and 3¡Á3 kernel. Results show that the SEG-LSTM model performs better than the other two temporal model.

@@

\subsection{Evaluation}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/evaluation.pdf}
        \caption{ {\small The evaluation of 2D and 3D prediction. 2D: It is the bounding box to cover the whole vehicle. 3D: The depth channel is combined with 2D bounding box to predict trajectory.}}
        \label{fig:evaluation}
\end{figure}
